\documentclass[10pt]{book} 
\usepackage{mathpazo}
\usepackage{geometry} 
\usepackage{titlesec} 
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx,subcaption}
\usepackage{float}
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}
\usepackage[colorlinks=true,linkcolor=blue, citecolor=blue]{hyperref}
\usepackage[authoryear,round]{natbib}

\usepackage{titlesec}

% Adjust spacing for chapters
\titlespacing*{\chapter}{0pt}{-50pt}{20pt}

% Adjust spacing for sections
\titlespacing*{\section}{0pt}{20pt}{10pt}


% Remove paragraph indentation and add space between paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}

\geometry{left=1.25in, right=1in, top=1in, bottom=1in, footskip=0.5in}

\titleformat{\chapter}[display]
{\normalfont\Large\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Large}
\titleformat{\section}
{\normalfont\large\bfseries}{\thesection}{1em}{}

\title{A Comprehensive Note on Machine Learning\footnote{This content serve only for \textbf{educational} and \textbf{personal} purpose, \textbf{do not share} without my approval.}}
\author{Jue Guo}
\date{\today}

\begin{document}
\frontmatter
\maketitle
\tableofcontents
\chapter*{Preface}

The primary purpose of this document is educational, specifically for the courses I teach (\textbf{CSE 474/574 Introduction to Machine Learning, CSE 455/555 Pattern Recognition, and CSE 676 Deep Learning}), as well as for my personal reference. A substantial portion of the material herein is directly referenced or adapted from established texts and sources, and is not claimed as original content. This document is intended as a supplementary teaching and learning resource and is not authorized for commercial use, redistribution, or sale without my explicit consent.

The majority of the material referenced comes from the following sources:

{
\renewcommand{\labelenumi}{[\theenumi]}
\setcounter{enumi}{0} % Start enumeration from 1

\begin{enumerate}
	\item Zhang, Aston, et al. Dive into deep learning. Cambridge University Press, 2023.
	\item Bishop, C. M., \& Nasrabadi, N. M. (2006). Pattern recognition and machine learning (Vol. 4, No. 4, p. 738). New York: Springer.
	\item Hart, P. E., Stork, D. G., \& Duda, R. O. (2000). Pattern classification. Hoboken: Wiley.
	\item Burkov, A. (2019). The hundred-page machine learning book (Vol. 1, p. 32). Quebec City, QC, Canada: Andriy Burkov.
	\item Burkov, A. (2020). Machine learning engineering (Vol. 1). Montreal, QC, Canada: True Positive Incorporated. \footnote{This is a birthday present from my lab member and good friend Peiyao Xiao}
\end{enumerate}
}

All other referenced materials and sources are cited in the bibliography section of this document. This compilation is intended to provide a comprehensive overview and guide for students and practitioners of machine learning, drawing upon a wide range of foundational and contemporary sources in the field.

\mainmatter
\part{Basic Machine Learning}
\include{Basic_Machine_Learning/introduction}
\include{Basic_Machine_Learning/notation}

\part{Advance Machine Learning}
\part{Convolution Neural Networks}

\part{Adversarial Attacks and Training}
\include{Adversarial_Attack_and_Training/intriguing_properties_of_NN}

\part{Recurrent Neural Networks}

\part{Transformers}

\part{Artificial General Intelligence}
\include{Artificial_General_Intelligence/continual_learning}
\include{Artificial_General_Intelligence/ER_AML}

\backmatter
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
